IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/conclusion.tex

We presented a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We prove the security guarantees
TSNI and TINI, where the proof technique is parametrized on the
target language, for two scheduling policies. In
addition, we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice. Finally, we described extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notation of clearance, and therefore connecting it with existing
IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C.

>>>>

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single language.  We showed
how to prove systems designed this way can be proved noninterferent,
without needing to rely on details of the target language, and
we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice.  We connected our semantics
to existing IFC implementations for JavaScript and Haskell, and proposed
an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to programming languages,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.

### 2014-07-08 paper/concrete.tex

\item When we clone the heap, we have to create a copy of everything
reachable from the sandboxed expression (not just the values for
the memory addresses in the expression), and replace all addresses
correspondingly.  Even worse, the behavior of sending a memory address
now depends on whether that address existed at the time the receiving
task was sandboxed;  if it did, then the address should be rewritten to the
new one, otherwise to a fresh address.
\end{itemize}

>>>>

\item When we clone the heap, we have to copy everything
reachable from the sandboxed expression and replace all addresses
correspondingly.  Even worse, the behavior of sending a memory address
now depends on whether that address existed at the time the receiving
task was sandboxed;  if it did, then the address should be rewritten to the
existing one.
\end{itemize}

### 2014-07-08 paper/extensions.tex

While the IFC language presented thus far provides the basic
information flow primitives, actual IFC implementations
may wish to extend the minimal system with more specialized
constructs.
%Different concrete IFC implementations may wish to extend our minimal
%system with labeled constructs appropriate for their envisioned
%applications.
%%
For example, COWL provides a labeled version of the XHR object, while
LIO implements a labeled file system, used in server-side web
applications~\cite{hails}.
%%
%Below we
%consider the addition of several labeled constructs to the abstract specification.
In this section we show how to extend the language with several such
constructs.
%
%We remark that that the non-interference proofs must account for the
%new constructs, since they amend the IFC calculus semantics (usually
%by addition).

@@

If such fine-grained labeling of values is required, our base IFC
system can be extended with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |iv ::= cdots
inlinesep Labeled il ie|.
%
Following LIO, we say that the expression |ie| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
The label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |ie|, it
must first raise its label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%

Full details with formal reduction rules are provided
in \appendixextfirst{}, but omitted here for space reasons.
%}

\subsection{Labeled mutable references/variables/channels}
%
Extending the calculus with other labeled features, such as
references, mutable variables (MVars)~\cite{CH96}, or channels,
can be done in a similar manner: these references are implemented
in the IFC language, separately from any preexisting notions of
mutable references in the target language.
%
%While we can modify the IFC calculus to add such labeled state to each
%individual task, adding it to the system state |iS| leads to more
%interesting use cases.
%
There is some minor additional state to track: specifically, by amending |iS|, as in~\cite{lio,
stefan:addressing-covert}, we can allow threads to use these
constructs to synchronize, or communicate with constructs other than
|send|/|recv| in a safe manner.
%
For example, when extending the calculus with labeled references, |iS|
additionally contains a store that maps addresses to a value
and a label
which can be read and written to by different tasks through a labeled
reference implementations.
Again, we omit details here and refer the interested reader
to \appendixext{}, where this extension has been fully worked out.

@@

\Red{TODO: provide them in the appendix, and refer to them here.}

>>>>

While the IFC language presented thus far provides the basic
information flow primitives, actual IFC implementations
may wish to extend the minimal system with more specialized
constructs.
%Different concrete IFC implementations may wish to extend our minimal
%system with labeled constructs appropriate for their envisioned
%applications.
%%
For example, COWL provides a labeled version of the XHR object, while
LIO implements a labeled file system, used in server-side web
applications~\cite{hails}.
%%
%Below we
%consider the addition of several labeled constructs to the abstract specification.
In this section we show how to extend the language with several such
constructs.  For space reasons, we mainly provide the high-level
ideas here, and provide full formal semantics (including the soundness
proof with the extensions) in \appendixextfirst{}.
%
%We remark that that the non-interference proofs must account for the
%new constructs, since they amend the IFC calculus semantics (usually
%by addition).

@@

If such fine-grained labeling of values is required, our base IFC
system can be extended with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |iv ::= cdots
inlinesep Labeled il ie|.
%
Following LIO, we say that the expression |ie| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
The label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |ie|, it
must first raise its label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%
%}

\subsection{Labeled mutable references/variables/channels}
%
Extending the calculus with other labeled features, such as
references, mutable variables (MVars)~\cite{CH96}, or channels,
can be done in a similar manner: these references are implemented
in the IFC language, separately from any preexisting notions of
mutable references in the target language.
%
%While we can modify the IFC calculus to add such labeled state to each
%individual task, adding it to the system state |iS| leads to more
%interesting use cases.
%
There is some minor additional state to track: specifically, by amending |iS|, as in~\cite{lio,
stefan:addressing-covert}, we can allow threads to use these
constructs to synchronize, or communicate with constructs other than
|send|/|recv| in a safe manner.
%
For example, when extending the calculus with labeled references, |iS|
additionally contains a store that maps addresses to a value
and a label
which can be read and written to by different tasks through a labeled
reference implementations.

@@
